SoK: Defending Against Web Application Attacks: From Research Approaches to Practical Tools

### 2014-11-15 docs/questioning.tex
pass in abstract

  Some of the most dangerous web application attacks, such as Cross-Site
  Scripting and SQL injection, exploit vulnerabilities
  in web applications that may accept and process
  data of uncertain origin without proper validation or
  filtering, allowing the injection and execution of
  dynamic or domain-specific language code.
  These attacks have been constantly topping the lists of
  various security bulletin providers despite the numerous
  countermeasures that have been proposed over the past 15 years.

  In this paper, we systematize the existing knowledge on
  various defense mechanisms against code injection attacks by proposing
  a model that highlights the key weaknesses that enable these attacks,
  and provides a common perspective for the different defenses.
  We then categorize and analyze the various defense mechanisms that
  have been developed, based on their accuracy, performance,
  deployment, security, and availability properties.
  Accuracy is of particular importance, as our findings show that many defense
  mechanisms have been tested in a poor manner. In addition, we observe
  that some mechanisms can be bypassed by attackers with knowledge
  of how the mechanisms work. Finally, we discuss the results
  of our analysis, with emphasis on factors that may hinder
  the widespread adoption of attack detection mechanisms
  in practice.

@@

\begin{IEEEkeywords}
Protection Mechanisms, Web Application Security, Code injection Attacks,
Testing, Cross-Site Scripting.
\end{IEEEkeywords}

>>>>

  Some of the most dangerous web attacks, such as Cross-Site
  Scripting and SQL injection, exploit vulnerabilities
  in web applications that may accept and process
  data of uncertain origin without proper validation or
  filtering, allowing the injection and execution of
  dynamic or domain-specific language code.
  These attacks have been constantly topping the lists of
  various security bulletin providers despite the numerous
  countermeasures that have been proposed over the past 15 years.

  In this paper, we systematize the existing knowledge on
  various defense mechanisms against web injection attacks. We propose
  a model that highlights the key weaknesses enabling these attacks,
  and that provides a common perspective for studying the available defenses.
  We then categorize and analyze a set of 35 previously proposed defenses 
  based on their accuracy, performance,
  deployment, security, and availability characteristics.
  Detection accuracy is of particular importance,
  as our findings show that many defense
  mechanisms have been tested in a poor manner. In addition, we observe
  that some mechanisms can be bypassed by attackers with knowledge
  of how the mechanisms work. Finally, we discuss the results
  of our analysis, with emphasis on factors that may hinder
  the widespread adoption of defenses in practice.

@@

\begin{IEEEkeywords}
Protection mechanisms, web application security,
SQL injection, XSS, CSRF.
\end{IEEEkeywords}
